Main Figures

### 2021-02-01 figure_manuscript/codes_of_figures.Rmd
reproducible codes of figures

-----------------
## Network construction with overall functional annotation: Additional figure important genes from functional Annotation

@@

```{r, warning=FALSE}
mirtarbase_node_perturbations%>%
  left_join(gene_dist, by = "name")%>%
  mutate(tissue_type = ifelse(endsWith(file_name, "01A"), "Tumor", "Normal"),
         node_type = ifelse(name %in% effective_nodes$name, "effective", "non_effective"))%>%
  filter(node_type == "effective", perturbed_count > 78, perturbed > 10)%>%
  filter(tissue_type != "Normal", startsWith(name, "hsa"))%>%
  dplyr::select(file_name, name,tissue_type, perturbed_count)->mirna_tumor

mirtarbase_node_perturbations%>%
  left_join(gene_dist, by = "name")%>%
  mutate(tissue_type = ifelse(endsWith(file_name, "01A"), "Tumor", "Normal"),
         node_type = ifelse(name %in% effective_nodes$name, "effective", "non_effective"))%>%
  filter(node_type == "effective", perturbed_count > 78, perturbed > 10)%>%
  filter(tissue_type == "Normal", startsWith(name, "hsa"))%>%
  dplyr::select(file_name, name,tissue_type, perturbed_count)->mirna_normal

@@

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=9,fig.show='hold'}
mirna_tumor%>%
  full_join(mirna_normal, by =c("name", "file_name"), suffix= c("_tumor", "_normal"), fill.na = 0)%>%
  dplyr::select(-3, -5)%>%
  mutate(perturbed_count_tumor = ifelse(is.na(perturbed_count_tumor), 1, perturbed_count_tumor),
         perturbed_count_normal = ifelse(is.na(perturbed_count_normal), 1, perturbed_count_normal),
         log_FC= log2(perturbed_count_tumor/perturbed_count_normal))%>%
  ggplot(aes(x = file_name, y = name, fill = log_FC))+
  geom_tile(aes(colour = log_FC, fill = log_FC))+
  theme_test()+
  theme(axis.text.x = element_blank(), #element_text(angle = 90, vjust = 0, hjust=0)
        plot.title = element_text(hjust = 0.5))+
  scale_colour_gradientn(colours = c("green","white", "red"), aesthetics = c("colour", "fill"), na.value = "grey")+
  ylab("Highly pertubing miRNA nodes")+
  xlab("Patients")+
  theme( legend.title = element_blank(), panel.background = element_rect(fill = "white"))

@@

mirna_tumor%>%
  full_join(mirna_normal, by =c("name", "file_name"), suffix= c("_tumor", "_normal"), fill.na = 0)%>%
  dplyr::select(-3, -5)%>%
  pivot_longer(cols = c("perturbed_count_tumor", "perturbed_count_normal"), names_to = "situ", values_to = "perturbed_count")%>%
  mutate(perturbed_count_log = log2(perturbed_count),
         situ = str_replace(situ, "perturbed_count_normal", 'Perturbed count in normal'),
         situ = str_replace(situ, "perturbed_count_tumor", 'Perturbed count in tumor'),
         perturbed_count = as.numeric(str_replace_na(perturbed_count, 0)),
         perturbed_count_log = as.numeric(str_replace_na(perturbed_count_log, 0)))%>%
  ggplot(aes(x = file_name, y = name, fill = perturbed_count_log))+
  geom_tile(aes(colour = perturbed_count_log, fill = perturbed_count_log))+
  theme_test()+
  theme(axis.text.x = element_blank(), #element_text(angle = 90, vjust = 0, hjust=0)
        plot.title = element_text(hjust = 0.5))+
  scale_colour_gradientn(colours = c("green","red", "black"), aesthetics = c("colour", "fill"), na.value = "grey")+
  ylab("Highly pertubing miRNA nodes")+
  xlab("Patients")+
  facet_grid(rows = "situ")+
  theme( legend.title = element_blank(), panel.background = element_rect(fill = "gray93"))

>>>>

----------------- This figure was removed from manuscript.
## Network construction with overall functional annotation: Additional figure important genes from functional Annotation

@@

```{r, warning=FALSE}
mirtarbase_node_perturbations%>%
  left_join(gene_dist, by = "name")%>%
  mutate(tissue_type = ifelse(endsWith(file_name, "01A"), "Tumor", "Normal"),
         node_type = ifelse(name %in% effective_nodes$name, "effective", "non_effective"))%>%
  filter(node_type == "effective", perturbed_count > 78, perturbed > 10)%>%
  filter(tissue_type != "Normal", startsWith(name, "hsa"))%>%
  mutate(file_name= str_remove(file_name, "-01A"))%>%
  dplyr::select(file_name, name,tissue_type, perturbed_count)->mirna_tumor

mirtarbase_node_perturbations%>%
  left_join(gene_dist, by = "name")%>%
  mutate(tissue_type = ifelse(endsWith(file_name, "01A"), "Tumor", "Normal"),
         node_type = ifelse(name %in% effective_nodes$name, "effective", "non_effective"))%>%
  filter(node_type == "effective", perturbed_count > 78, perturbed > 10)%>%
  filter(tissue_type == "Normal", startsWith(name, "hsa"))%>%
  mutate(file_name= str_remove(file_name, "-11A"))%>%
  dplyr::select(file_name, name,tissue_type, perturbed_count)->mirna_normal

@@

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=9,fig.show='hold'}
mirna_tumor%>%
  full_join(mirna_normal, by =c("name", "file_name"), suffix= c("_tumor", "_normal"), fill.na = 0)%>%
  dplyr::select(-3, -5)%>%
  mutate(perturbed_count_tumor = ifelse(is.na(perturbed_count_tumor), 1, perturbed_count_tumor),
         perturbed_count_normal = ifelse(is.na(perturbed_count_normal), 1, perturbed_count_normal),
         log_FC= log2(perturbed_count_tumor/perturbed_count_normal))%>%
  ggplot(aes(x = file_name, y = name, fill = log_FC))+
  geom_tile(aes(colour = log_FC, fill = log_FC))+
  theme_test()+
  theme(axis.text.x = element_blank(), #element_text(angle = 90, vjust = 0, hjust=0)
        plot.title = element_text(hjust = 0.5))+
  scale_colour_gradientn(colours = c("green","white", "red"), aesthetics = c("colour", "fill"), na.value = "grey")+
  ylab("Highly pertubing miRNA nodes")+
  xlab("Patients")+
  theme( legend.title = element_blank(), panel.background = element_rect(fill = "white"),  plot.margin = margin(0, 0, 0, 0, "cm"))

ggsave(filename = 'mirna_comparison.svg', width = 8, height = 4)

@@

mirna_tumor%>%
  full_join(mirna_normal, by =c("name", "file_name"), suffix= c("_tumor", "_normal"), fill.na = 0)%>%
  dplyr::select(-3, -5)%>%
  pivot_longer(cols = c("perturbed_count_tumor", "perturbed_count_normal"), names_to = "situ", values_to = "perturbed_count")%>%
  mutate(perturbed_count_log = log2(perturbed_count),
         situ = str_replace(situ, "perturbed_count_normal", 'Perturbed count in normal'),
         situ = str_replace(situ, "perturbed_count_tumor", 'Perturbed count in tumor'),
         perturbed_count = as.numeric(str_replace_na(perturbed_count, 0)),
         perturbed_count_log = as.numeric(str_replace_na(perturbed_count_log, 0)))%>%
  ggplot(aes(x = file_name, y = name, fill = perturbed_count_log))+
  geom_tile(aes(colour = perturbed_count_log, fill = perturbed_count_log))+
  theme_test()+
  theme(axis.text.x = element_blank(), #element_text(angle = 90, vjust = 0, hjust=0)
        plot.title = element_text(hjust = 0.5))+
  scale_colour_gradientn(colours = c("green","red", "black"), aesthetics = c("colour", "fill"), na.value = "grey")+
  ylab("Highly pertubing miRNA nodes")+
  xlab("Patients")+
  facet_grid(rows = "situ")+
  theme( legend.title = element_blank(), panel.background = element_rect(fill = "gray93"),  plot.margin = margin(0, 0, 0, 0, "cm"))

ggsave(filename = 'mirna_comparison_normal_tumor.svg', width = 8, height = 7)
```
